---
title: "geo facet"
author: "Ray Wright"
date: "`r Sys.Date()`"
output:
  html_document:
    css: map_facet.css
---

```{r setup, include=FALSE}
# https://blog.rstudio.org/2015/12/10/svglite-1-0-0/
library(svglite)
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  out.width = 1100,
  out.height = 800,
  fig.width = 12,
  fig.height = 9,
  dev = "svglite",
  fig.ext = ".svg"
)
```

## Intro

Use the geofacet package to create a PA county grid of plots, similar to examples from https://hafen.github.io/geofacet/.

## Data

Use custom-made Pennsylvania county grid and data from EDDIE.

```{r}
library(tidyverse)
library(stringr)
library(geofacet)
library(plotly)

# https://hafen.github.io/grid-designer/
pa_counties_grid = read_csv("pa_counties_grid.csv") %>% 
  filter(!is.na(row))

cw_county = read_csv("cw_county.csv")

data_death = read_csv(
  "death_death.csv",
  col_types = cols_only(
    CauseofDeaths = col_character(),
    CountyState = col_character(),
    Year = col_character(),
    RateRatio = col_double(),
    LowerBound = col_double(),
    UpperBound = col_double()
  ),
  skip = 3
) 

data_death_2 = data_death %>% 
  filter(CountyState != "Pennsylvania") %>% 
  mutate(year_last = as.integer(str_sub(Year, 6, 9))) %>% 
  left_join(cw_county, by = c("CountyState" = "name"))
```

## US states - geofacet

This is a slightly modified example from https://hafen.github.io/geofacet/.

```{r}

color_line = "#1f77b4"

ggplot(state_unemp) +
  geom_line(aes(year, rate), color = color_line, size = 1) +
  facet_geo(~state, grid = "us_state_grid2", label = "name") +
  scale_x_continuous(labels = function(x) paste0("'", substr(x, 3, 4))) +
  labs(
    title = "Seasonally Adjusted US Unemployment Rate 2000-2016",
    x = "",
    y = "Unemployment Rate (%)"
  ) +
  theme_bw() +
  theme(strip.text.x = element_text(size = 7))

```

## PA counties - geofacet

This is my unfinished example using EDDIE data and my custom PA county grid.

```{r}

ggplot(data_death_2) +
  geom_line(aes(year_last, RateRatio), color = color_line, size = 1) +
  # geom_hline(aes(yintercept = 0)) +
  scale_x_continuous(breaks = c(2000, 2005, 2010, 2015)) +
  scale_y_continuous(limits = c(-1.5, 31.5)) +
  labs(
    title = "Drug overdose deaths, 2003-2015, 5-year moving average",
    x = "",
    y = "Age-adjusted death rate"
  ) +
  facet_geo(~code, grid = pa_counties_grid, label = "name") + 
  theme_bw()
  
```

## PA counties - plotly

This is my unfinished example using plotly.

```{r}

plot_county = function(x) {
  plot_data = filter(data_death_2, CountyState == x)
  plot_ly(plot_data) %>% 
    add_lines(
      ~year_last,
      ~RateRatio,
      line = list(color = color_line, width = 3)
    ) %>% 
    layout(
      margin = list(l = 40, r = 40),
      showlegend = FALSE,
      xaxis = list(title = FALSE),
      yaxis = list(title = FALSE, range = c(-1.5, 31.5))
    )
}

map(cw_county$name, plot_county) %>% 
  subplot(
    nrows = 7,
    margin = 0.01,
    widths = c(0.092, rep(0.102, 8), 0.092),
    heights = c(0.1357, rep(0.1457, 5), 0.1357),
    shareX = TRUE,
    shareY = TRUE
  )

```
